A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\uline{We utilize this Iterative Target Class Method to update our perturbation values during the training process. To achieve a balance between the attack efﬁciency and the perturbation perceptibility, we constrain the perturbation values in the loss function of Eq.~(10) instead of using the clip operation. At each training step, our perturbations are updated as follows:}
\begin{equation}
\renewcommand\theequation{14}
\delta_{k+1} = \delta_{k} - \epsilon_1 \cdot \text{sign}(\nabla_{\delta_k}L)
\end{equation}
\begin{equation}
\renewcommand\theequation{15}
p_{k+1} = p_{k} - \epsilon_2 \cdot \text{sign}(\nabla_{p_k}L),
\end{equation}

\textit{3. The descriptions of figures and tables are not self-explanatory.}

\textbf{Thanks for your advice and we have rewritten the descriptions of figures and tables. The modification is shown as follows for the convience of cross checking.}

@@

% figure 4
\textbf{In Figure 4, we have replaced ``Results of targeted attacks where the tracker is forced to follow a predefined \textit{fake trajectory} (indicated by the yellow targeted bounding box).'' with}
\uline{``Results of targeted attacks where the tracker is forced to follow a predefined \textit{fake trajectory} $B^{fake}=\{b^{fake}_i\}_1^{T}$ (indicated by the yellow bounding boxes). The \textit{fake trajectory} follows the real trajectory $B^{gt}=\{b^{gt}_i\}_1^T$ (indicated by the red bounding boxes) except that the adjacent boundaries of $b^{fake}_i$ and $b^{gt}_i$ are 2 pixels apart.''}

\textit{4. I suggest adding the advantages \& limitations of the proposed method after experimental analysis and future works to the conclusion.}

\textbf{Thanks for the good commenet. As suggested, we have added the advantages \& limitations of the proposed method after experimental analysis and future works to the conclusion. For your convenience in cross-checking, the new text is given as follows.}

\uline{In summary, compared with other attack methods, our method has two key advantages. First, the proposed attack method only needs to perform the addition operations to deploy the adversarial information for any novel video without gradient optimization or network inference, making it possible to attack a real-world online-tracking system when we can not get access to the limited computational resources. Second, the proposed perturbations show good transferability to other anchor-free or anchor-based trackers. The main limitation of our work is that the translucent perturbations my result in suspicious attacks.}

\uline{In the future work, we expect that it will be possible to further reduce the possible suspicion by increasing the perturbation's imperceptibility while maintaining the attack efficiency.}

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

%%%% 问题 2.4 %%%%
\textit{4. As reviewer 1 and reviewer 2 say, the perturbations added to template regions and research regions are not imperceptible, which may be helpful to misguide the tracker. The reviewer considers that adding a similar random pattern on the template and search regions to further illustrate the effectiveness of the proposed method.}

\textbf{To further illustrate the effectiveness of our proposed method, we manually generate similar random patterns and add them on the template and search regions (see Fig. \ref{fig:random}) to show their attack performance. 
Specifically, we design two kinds of random patterns: (1) the random pattern similar to our trained perturbations, and (2) the random pattern generated using zero-mean Gaussian noise with standard deviation 50.0.
We replace the trained perturbations with the above random patterns to attack SiamFC++\_GoogleNet, and experimentally evaluate them on GOT-Val.
As shown in Table \ref{table:noise}, these random patterns cannot effectively attack the tracker.
For your convenience in cross-checking, the new text is given as follows.
}

\begin{table}[t]
  \renewcommand\thetable{VII}
  \centering
  \caption{Attack performance comparison using other random patterns. It is evaluated on GOT-Val.}
  \label{table:noise}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Perturbations used to \\ perfrom attack \end{tabular}} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack}\\ \cmidrule{2-5}
                                                         & AO                                      & SR                               & AO                & SR                  \\ \midrule
  Trained Perturbations                                  & 0.153                                   & 0.123                            & 0.840             & 0.890               \\
  Similar Pattern                                         & 0.736                                   & 0.871                            & 0.153             & 0.118               \\
  Gaussian Noise                                         & 0.740                                   & 0.875                            & 0.144             & 0.101               \\ \bottomrule        
  \end{tabular}
\end{table}
\begin{figure}[t]
  \renewcommand\thefigure{9}
  \centering
  \includegraphics[width=0.8\textwidth]{images_imperceptible/random_gaussian.pdf}
  \caption{Visualization of the manually generated similar random patterns.}
  \label{fig:random}
\end{figure}
\uline{\textit{Use Other Similar Random Patterns.} ~To further illustrate the effectiveness of our proposed method, we manually generate similar random patterns and add them on the template and search regions (see Fig. \ref{fig:random}) to show their attack performance. 
Specifically, we design two kinds of random patterns: (1) the random pattern similar to our trained perturbations, and (2) the random pattern generated using zero-mean Gaussian noise with standard deviation 50.0.
We replace the trained perturbations with the above random patterns to attack SiamFC++\_GoogleNet, and experimentally evaluate them on GOT-Val.
As shown in Table \ref{table:noise}, these random patterns cannot effectively attack the tracker.
}

@@

\textbf{We have added the definition of $b_{\textbf{x}}^{fake}$ of Eq.4 as follows:}
``\uline{$b_{\textbf{x}}^{fake} = \{x_0, y_0, x_1, y_1\}$ denotes the coordinates of the upper-left and lower-right corners of the fake target on the search image.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have replaced ``In SiamFC++, the tracker first transforms the paired reference frame $I_1$ and annotation $b_1^{gt}$ to get an template image $\textbf z_1$, and transforms the search frame $I_i$ to get the search image $\textbf x_i$ centered at the position estimated in the previous frame.'' with}
``\uline{In SiamFC++, the tracker first transforms the paired reference frame $I_1$ and annotation $b_1^{gt}$ to get a template image $\textbf z_1$, and transforms the search frame $I_i$ to get the search image $\textbf x_i$ centered at the position estimated in the previous frame.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have replaced ``However, CNN attacks are usually expected imperceptible but the above method has to paste an obviously noticeable fake target patch to tracking frames, which raises the risk of being suspected.'' with}
``\uline{However, CNN attacks are usually expected to be imperceptible whereas the above method has to paste an obviously noticeable \textit{fake target} patch into tracking frames, which raises the risk of being suspected.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have  replaced ``$A_add$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},$ $\frac{y_0+y_1}{2})$.'' with}
``\uline{$A_{add}$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$.}''
\textbf{in Section III.B of the revised manuscript.}

@@

\textbf{Thanks for your advice and we have rewritten the descriptions of figures and tables. The modification is shown as follows for the convience of cross checking.}

\textbf{In Table IV, we have replaced ``Compared with baselines on perturbed GOT-Val dataset.'' with}
\uline{``Comparison of attack performance with 2 baseline methods on GOT-Val in terms of AO. Baseline-1 performs untargeted attacks based on the UAP [9] method. Baseline-2 performs targeted attacks based on the adversarial patch [50] method.''}
\textbf{in Section IV.D of the revised manuscript.}

\textbf{In Table IX, we have replaced ``Contribution of each loss on GOT-Val.'' with}
\uline{``Analysis of the impact of each loss component on GOT-Val.''}
\textbf{in Section IV.E of the revised manuscript.}

\textbf{In Table XII, we have replaced ``Transferability to different backbones on GOT-Val.'' with}
\uline{``Transferability to different backbones of our perturbations trained on SiamFC+}
\uline{+\_GoogleNet. It is evaluated on GOT-Val.''}
\textbf{in Section IV.F of the revised manuscript.}

\textbf{In Table XIII, we have replaced ``Transferability to different tracking architectures on OTB2015.'' with}
\uline{``Transferability to different tracking architectures of our pertur-
bations trained on SiamFC++\_GoogleNet. It is evaluated on OTB2015.''}
\textbf{in Section IV.F of the revised manuscript.}

@@

\textbf{We have discussed several state-of-the-art anchor free Siamese trackers at the related work. For your convenience of cross review, the new text is given as follows.}

\uline{In this anchor-free paradigm, many recent works (e.g., [20], [21], [22]) are dedicated to more robust and efficient visual tracking based on various anchor-free settings.
% Ocean
Ocean [20] directly predicts the position and scale of target objects in an anchor-free fashion; since each sample position in groundtruth boxes is well trained, the tracker is capable of rectifying inexact predictions of target objects during inference.
% FCOT
FCOT [21] introduces an online regression model generator (RMG) based on the carefully designed anchor-free box regression branch, which enables the tracker to be more effective in handling target deformation during tracking procedure.
%  SiamCAR
SiamCAR [22] is both anchor and proposal free, and takes one unique response map to predict object location and bounding box directly; this setting significantly reduces the number of hyper-parameters, which keeps the tracker from complicated parameter tuning and makes the tracker significantly simpler, especially in training.
}

\textbf{Besides, we have evaluated the transferability to the anchor free tracker OCEAN in Setcion IV.F of the revised manuscript. For your convenience of cross review, the new text is given as follows.}

\begin{table}[t]
  \renewcommand\thetable{XIII}
  \centering
  \caption{Transferability to different tracking architectures of our perturbations trained on SiamFC++\_GoogleNet. It is evaluated on OTB2015.}
  \begin{tabular}{rcccc} 
  \toprule
  \multirow{2}{*}[-2pt]{Trackers} & \multicolumn{2}{c}{Before Attack} & \multicolumn{2}{c}{Untargeted Attack}  \\
  \cmidrule{2-5}
                            & AO & Precision              & AO    & Precision \\ \midrule
  SiamRPN++ [24]            & 0.676   & 0.879             & 0.418 & 0.556     \\
  SiamRPN [23]              & 0.666   & 0.876             & 0.483 & 0.643     \\
  Ocean [20]                & 0.672   & 0.902             & 0.237 & 0.282     \\ \bottomrule
  \end{tabular}
  \label{tab:arch}
\end{table}
\uline{\textit{Transferability to Different Tracking Architectures.} We also evaluate the transferability of our attacks when applying the perturbations to three more state-of-the-art trackers: SiamRPN [23], SiamRPN++ [24] and Ocean [20]. SiamRPN and SiamRPN++ are anchor-
based trackers, and Ocean is an anchor-free tracker. The experimental results are shown in Table \ref{tab:arch}. In the case of SiamRPN, the AO with respect to the real trajectory decreases from 0.666 to 0.483 and the performance of SiamRPN++ is decreased from 0.676 to 0.418. In the case of Ocean, the AO with respect to the real trajectory decreases from 0.902 to 0.282. The results show good transferability of our attacks to different tracking architectures, even if the generated perturbations are applied to anchor-based trackers.
}

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textbf{Sorry for the inconvenience of reading Fig. 9 caused by the small font size.
We are willing to adjust Fig. 9 font size to make it easier to read on the computer, but because we have added many ablation experiments to revised manuscript, the total number of pages exceeds the maximum page limit for TCSVT (i.e., 14 pages). Therefore we have to remove the analysis of the attack performance for each attribute of the OTB as well as Fig. 9.
}

%%%% 问题 1.4 %%%%
\textit{Also, some recent papers are valued to be referred (2020-2021), to enhance the quality.}

\textbf{Thanks for the good comments. We have added several 2020-2021 related papers to enhance the quality of the revised manuscript. For your convenience of cross review, the new text is given as follows.}

\uline{Recently, some Siamese trackers [10], [20], [21], [22], [23], [24] have demonstrated a significant performance improvement in visual tracking.}

@@

\uline{
$A_{\text{paste}}$ means that, in the region where the perturbation is pasted, the pixel values of the original image are \textit{replaced} with the pixel values of the perturbation.
The operator $A_\text{add}$ refers to the injection of our translucent adversarial patch into the search image, \ie, the values of our translucent adversarial patch are \textit{added} to the pixel values of the original image in the $b^{fake}_{\textbf{x}}$ area.}

\uline{
The adversarial patch is usually added to the background region of the search image and does not change the pixel values in the foreground region where the real target exists. Therefore if we do not add additional perturbation to the template image, the response values of the region where the real target exists on the heatmaps are always high. Thus it is necessary to perturb the template image to cooling down hot regions where the real target exists on the heatmaps and increasing the responses at the position of the \textit{fake target}.
}

\textbf{To further analyze the impact of $p$ and $\delta$ in our perturbations, we evaluate the attack performance when only adding perturbations on the template images or the search regions on GOT-Val. The detailed analysis of new added experiment is added in Section IV.E of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textit{- The reinitialization of VOT-toolkit should be mentioned in the part of ‘experimental setup’.}

\textit{- On page 7, ‘.(see Table I)’ is a typo.}

\textbf{Thanks for the good comment. We have carefully checked through the whole text and corrected the grammar mistakes and typos. Specifically,}
\textbf{We have replaced ``Experiment results on OTB2015 [11], GOT-10k [12], LaSOT [12], UAV123 [13], VOT1016 [14], VOT2018 [15] and VOT2019 [16]. benchmarks demonstrate the effectiveness and efficiency of our approach.'' with}
``\uline{Experiment results on OTB2015 [11], GOT-10k [12], LaSOT [13], VOT2016 [14], VOT2018 [15] and VOT2019 [16] benchmarks have demonstrated the effectiveness and efficiency of our approach.}''
\textbf{in Section I of the revised manuscript.}

\textbf{We have added the definition of $b_{\textbf{x}}^{fake}$ of Eq.4 as follows:}
``\uline{$b_{\textbf{x}}^{fake} = \{x_0, y_0, x_1, y_1\}$ denotes the coordinates of the upper-left and lower-right corners of the fake target on the search image. $y^{fake}$ is generated according to $b^{fake}_{\textbf{x}}$ and both of them are variables during training.}''
\textbf{in Section III.A of the revised manuscript.}

@@

\textbf{In Table XIII, we have replaced ``Transferability to different tracking architectures on OTB2015.'' with}
\uline{``Transferability to different tracking architectures of our pertur-
bations trained on SiamFC++\_GoogleNet. It is evaluated on OTB2015.''}
\textbf{in Section IV.F of the revised manuscript.}

% table 14
\textbf{In Table XIV, we have replaced ``Untargeted attack: Precision score on OTB2015.'' with}
\uline{``State-of-the-art comparison of untargeted attack performance on OTB2015 in terms of precision score.''}
\textbf{in Section IV.G of the revised manuscript.}

% table 15
\textbf{In Table XV, we have replaced ``Targeted attack: Precision score on OTB2015.'' with}
\uline{``State-of-the-art comparison of targeted attack performance on OTB2015 in terms of precision score.''}
\textbf{in Section IV.G of the revised manuscript.}

\textbf{In Figure 1, we have replaced ``Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations except the mere addition operations.'' with}
\uline{``Being universal, our generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra intensive computa-
tions except the mere addition operations.''}
\textbf{in Section I of the revised manuscript.}

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\begin{document}
\setstretch{1.5}
\linespread{1}
\title{Response to Reviewers of TCSVT-07024-2021: A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking}
\author{Zhenbang Li, Yaya Shi, Jin Gao, Shaoru Wang, \\Bing Li, Pengpeng Liang, Weiming Hu}
\date{}
\maketitle

\noindent Dear Editors:

We would like to express our heartfelt gratitude to you and the reviewers for the insightful and helpful comments. When we revised the paper, we carefully considered and followed all the comments and suggestions provided by you and the reviewers. To summarize, we have made the following revisions:

(1) We have carefully considered and followed all the comments and suggestions related to the clarity of the writing, and made the new material a thoroughly revised manuscript. Specifically, several state-of-the-art anchor-free trackers have been discussed in Section II. The algorithm for the attack process has been added in Section III.C. We have explained in detail the perturbation update process in offline training. We have also added the advantages and limitations of the proposed method after experimental analysis and the future work to the conclusion. The descriptions of figures and tables have been rewritten, and the format of all the tables has been unified.

(2) The experiments have also been thoroughly re-evaluated in Section IV. Specifically, we have added more experiments to demonstrate the practicability of the attack method when the ground truth box information is missing in the training data. Besides the strategy to generate the fake trajectory following the real trajectory in Sec. III, we have also considered an alternative way to generate the fake trajectory. To analyze the impact of our perturbations, we have evaluated the attack performance when only adding perturbations on the template images or the search regions on GOT-Val. To further illustrate the effectiveness of our proposed method, we manually generate similar random patterns and add them on the template and search regions to show their attack performance. To reduce the perceptibility of the perturbations, we have examined a new strategy to perturb the search image.

(3) We have added 3 papers published in the IEEE Transactions on Circuits and Systems for Video Technology, which are most closely related to our manuscript, and analysed what is distinctive/new about our current manuscript related to these previously published papers. For your convenience in cross-checking, the new text is given as follows.

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/正文/main.tex
改小错
加致谢

\textit{Influence of Different Training Loss Components.} We implement a series of experiments to analyze the contribution of each loss component. In Table \ref{tab:loss}, we report the attack results on the GOT-Val dataset. The AO score of the tracker with respect to the real trajectory decreases from 0.760 to 0.747 when adversarial information is generated using only quality assessment loss, indicating that quality assessment loss can cause a slight degradation in the performance of the tracker.
%This is because the perturbation information generated using quality assessment loss interferes with the tracker's ability to select the best target. 
However, the tracker's AO score with respect to the \textit{fake trajectory} is only 0.148, indicating that the perturbations generated using quality assessment loss alone can barely cause the tracker to follow the specified trajectory. When the adversarial information is generated using only regression loss, the AO score of the tracker with respect to the real trajectory decreases from 0.760 to 0.243, indicating that regression loss can cause a large degradation in the tracker's performance. This is because the perturbation information generated using regression loss corrupts the tracker's ability to predict the accurate bounding box position. When adversarial information is generated using only classification loss, the tracker's AO score decreases from 0.760 to 0.282 with respect to the real trajectory and the AO with respect to the \textit{fake trajectory} is up to 0.643. This is because the perturbation information generated using classification loss causes the tracker to localize to the fake target instead of the real target's location. In conclusion, all loss terms are beneficial, and the classification/regression term is more important than the quality assessment term.

@@

>>>>

\textit{Influence of Different Training Loss Components.} We implement a series of experiments to analyze the contribution of each loss component. In Table \ref{tab:loss}, we report the attack results on the GOT-Val dataset. The AO score of the tracker with respect to the real trajectory decreases from 0.760 to 0.747 when adversarial information is generated using only quality assessment loss, indicating that quality assessment loss can cause a slight degradation in the performance of the tracker.
%This is because the perturbation information generated using quality assessment loss interferes with the tracker's ability to select the best target. 
However, the tracker's AO score with respect to the \textit{fake trajectory} is only 0.148, indicating that the perturbations generated using quality assessment loss alone can barely cause the tracker to follow the specified trajectory.
%When the adversarial information is generated using only regression loss, the AO score of the tracker with respect to the real trajectory decreases from 0.760 to 0.243, indicating that regression loss can cause a large degradation in the tracker's performance. This is because the perturbation information generated using regression loss corrupts the tracker's ability to predict the accurate bounding box position. 
When adversarial information is generated using only classification loss, the tracker's AO score decreases from 0.760 to 0.282 with respect to the real trajectory and the AO with respect to the \textit{fake trajectory} is up to 0.643. This is because the perturbation information generated using classification loss causes the tracker to localize to the fake target instead of the real target's location. In conclusion, all loss terms are beneficial, and the classification/regression term is more important than the quality assessment term.

@@

\section*{Acknowledgments}
The authors would like to thank the reviewers for their constructive comments and suggestions.
